Automatic Singing Transcription

### 2023-12-02 report/paper.tex
more on whisperx and sort bib

\subsection{Whisper Word-Level Alignment}

@@

% \bibliographystyle{apalike}
% \bibliography{references}
\printbibliography
\end{multicols*}
\end{document}

>>>>

\subsection{Whisper and WhisperX Word-Level Alignment}

\subsubsection{Whisper}
Whisper a ASR model trained on a extremely large dataset of 680,000 hours of audio \citep{whisper}.
Instead of using self-supervised learning like in wav2vec 2.0, Whisper uses a weakly supervised
approach. This approach uses a large dataset of audio and text that is not high quality as many of
the smaller datasets. Instead the dataset was generated by scraping the internet for audio and
their corresponding transcriptions. Although Whisper did not improve the state-of-the-art on the
LibriSpeech dataset when compared against wav2vec 2.0, did achieve improvements and therefore
state-of-the-art results on the a variety of other speech datasets \citep{whisper}. The model
performs well in zero-shot scenarios so it can achieve good results without fine-tuning on the
target dataset \citep{whisper}. This is important for AST because there are so many genres and
types of music and it would be difficult to fine-tune on all of them.

\subsubsection{WhisperX}
The original Whisper model was also able to provide some timestamps but they were not the focus of
the paper. It was more of a proof of concept that the same model can be used for multiple tasks
\citep{whisper}. WhisperX is a model that was trained specifically for word-level alignment and
the speedup of the Whisper model \citep{whisperX}.

On the TED-LIUM dataset, a dataset of TED talks \cite{tedlium3}, WhisperX was able to acheive a
11.8x speedup over Whisper. This is comparable to wav2vec 2.0 which was a 10.3x speedup over
Whisper. However, WhisperX was also able to achieve a WER of 9.7 compared to the 10.5 WER from
Whisper and 19.8 WER from wav2vec 2.0 \citep{whisperX}. This is a significant improvement over
of speed with a slight increase in performance. This is important for AST because it would allow
for faster training and inference times.

For the word alignment task, WhisperX uses an external phoneme alignment approach to generate
word level timestamps using phoneme level timestamps \citep{whisperX}. The external phoneme
alignment model was actually a wav2vec 2.0 model that used Dynamic Time Warping (DTW) to align
the phonemes \citep{whisperX}. The first and last phonemes of each word were used to generate
the word level timestamps \citep{whisperX}.

The most important improvement of WhisperX over Whisper is VAD Cut \& Merge technique. This
technique uses a Voice Activity Detection (VAD) model to cut the audio into segments at low voice
activity sections. This decreases the hallucination of Whisper if a word was partly spoken in a
audio segment which lead to the slight increase in WER \citep{whisperX}. The speedup of WhisperX
was also due to this technique it allowed parallel processing of the audio segments where
Whisper had to process sequenctially \citep{whisperX}.

@@

\printbibliography

\end{multicols*}

\end{document}
